### 2017-03-27 ThesisText/background.tex
Adds detail about clustering

\TODO{Talk about clustering (See ind\_007 for things about this)}

@@

>>>>

@@

Beyond the classification tasks, clustering may be used in educational data.
The overall objective of clustering is to find groups of similar objects
within data. In the context of~\gls{edm} that may mean looking for groups of
students with similar characteristics without their Moodle usage habits.~\cite{ind_007,ind_008}
